Python as a machine learning language: experiences from the \textit{scikit-learn} project

### 2013-06-07 paper.tex
Pipelines

\newcommand{\Xtr}{\texttt{X\_tr}}
\newcommand{\Xte}{\texttt{X\_te}}
\newcommand{\ytr}{\texttt{y\_tr}}
\newcommand{\yte}{\texttt{y\_te}}

@@

A distinguishing feature of the \textit{scikit-learn} API is its ability to
compose new estimators from several base estimators. Composition mechanisms can
be used to combine typical machine learning workflows (e.g., feature extraction,
centering/scaling/normalization, feature selection, learning) into a single
object which is itself an estimator. Relying on duck typing, composed estimators
can be used wherever usual estimators can be used. In particular, they integrate
within model selection routines, allowing one to optimize at once every step of
a complex workflow. Composition of estimators can be done in two ways: either
sequentially through \texttt{Pipeline} objects or in a parallel fashion through
\texttt{FeatureUnion} objects.

@@

>>>>

@@

A distinguishing feature of the \textit{scikit-learn} API is its ability to
compose new estimators from several base estimators. Composition mechanisms can
be used to combine typical machine learning workflows into a single object which
is itself an estimator. Through duck typing, composed
estimators can be used wherever usual estimators can be used. In particular,
they integrate within model selection routines, allowing one to optimize at once
every step of a complex workflow. Composition of estimators can be done in two
ways: either sequentially through \texttt{Pipeline} objects or in a parallel
fashion through \texttt{FeatureUnion} objects.

\texttt{Pipeline} objects are used for chaining multiple estimators into a
single one. This is useful since a machine learning workflow typically involves
a fixed sequence of steps in processing data (e.g., feature extraction,
centering / scaling / normalization, feature selection, learning and making
predictions). For convenience reasons, those steps can be combined into a
pipeline such that \texttt{fit} and \texttt{predict} need to be called only once
to fit the whole sequence. A pipeline also allows for the hyper-parameters of
all the base estimators to be grid-searched all at once. From an API point of
view, a \texttt{Pipeline} object takes as input a sequence of $N$ estimators,
where all $N-1$ first are transformers and the last is either a predictor or a
transformer. Calling \texttt{fit} on the pipeline is the same as calling
\texttt{fit} on each estimator in turn, \texttt{transform} the input and then
pass it on to the next step. The pipeline exposes all the methods the last
estimator in the pipe exposes. That is, if the last estimator is a predictor,
the pipeline can be used itself as a predictor. If the last estimator is a
transformer, then the pipeline is itself a transformer.

\texttt{FeatureUnion} objects

@@

\textcolor{red}{TODO: rewrite + describe Scorer API}
